\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-24 doc/incertae_sedis.tex
Reorder and reformat.

The interpretation of the \emph{incertae sedis} annotation affects the supertree
    pipeline at three points:
\begin{enumerate}
    \item The subproblem decomposition step relies on identifying uncontested nodes.
    Thus, varying interpretations of whether or not an \emph{incertae sedis}
    taxon can be placed within another taxon without contesting that taxon
    will affect the subproblem decomposition.
    \item When solving each subproblem, how taxon is represented as a rooted
    split can affect the solution found.
    As described below, the \emph{incertae sedis} annotation affects the 
        exclude groups of rooted split encodings.
    \item The step of assigning names to the supertree is affected by the 
        operational phylogenetic definition of each name.
\end{enumerate}

>>>>

We seek a semantics for supertrees with \emph{incertae sedis }taxa
that satisfy the following properties:
\begin{enumerate}
    \item An \emph{incertae sedis} node may intrude into its siblings and their
descendants.
    \item The semantics of an \emph{incertae sedis} node does not depend on assigned ranks, but only on the tree.
    \item Semantics is based on deriving a rooted (partial) split for each branch of the taxonomy.
      % These could be goals, but maybe discuss them as side-effects:
      % Side effect #1. Don't interdigitate
      % Side effect #2. Allow placing A next to B, and then placing B within A. (See Fig. 6)
\end{enumerate}

The rooted split derived from a node $n$ serves to determine both when $n$ is in conflict
with an input tree, and to where to place the taxon name for $n$ on the resulting synthesis tree.
% Removed mention of incertae sedis possibly affecting subproblem decomposition.  It
% actually doesn't but that is surprising, and therefore kind of a result.
